 Displacement Tracking Matrix - Analysis of IDP situation in Iraq
========================================================

Based on the data currently available the objective is to build an index that will help prioritising the area of intervention for the CCM cluster.

The possible calculations are:

 - % of IDP hosted in communal settings / private settings 
 - # of IDP hosted in communal setting  
 - are idps  hosted in school building? as this has a disruptive impact on local population
 - are idps are already in camp (compared to other communal setting)
 - do they access services? (in priority FOOD, WATER, NFI) 
 - what is the # of IDP in a district compared to # of refugees?
 - # of IDP in a district compared to # of local inhabitans
 - when IDP have been displaced ? (i.e. date of displacement -> pre-june /post-june).
 - has the location previously received assistance
 - has shelter been defined as one of the priority need?

We will score each of the composite indicator and then apply some ponderation in order to generate a vulnerability rank for the locations.



## Where are IDPs?

```{r  echo=FALSE, fig.height = 8,fig.width = 12 , fig.align = 'center' }

source(analysis.R)
plotorigin

```



## Pattern of Arrival per month and area of asylum

```{r  echo=FALSE, fig.height = 8, fig.width = 12 , fig.align = 'center' }
plotgovmonth
```

Pattern of Arrival per month and area of origin

```{r  echo=FALSE, fig.height = 8, fig.width = 12 ,fig.align = 'center' }
plotoriginmonth
```



## 

```{r  echo=FALSE, fig.height = 9, fig.width = 12  }
mapcommunalmonthorigin
```



## 

```{r  echo=FALSE, fig.height = 9, fig.width = 12 }
mapcamphex
```


## 

```{r  echo=FALSE, fig.height = 9, fig.width = 12}
mapcommunalhex
```



## 
```{r  echo=FALSE, fig.height = 9, fig.width = 12 }
mapprioritycash
```



## 
```{r  echo=FALSE, fig.height = 9, fig.width = 12 }
mapprioritychild
```



## 
```{r  echo=FALSE, fig.height = 9 , fig.width = 12}
mappriorityfood
```



## 
```{r  echo=FALSE, fig.height = 9, fig.width = 12 }
mappriorityhealth
```



## 

```{r  echo=FALSE, fig.height = 9 , fig.width = 12}
mapprioritynfi
```



## 

```{r  echo=FALSE, fig.height = 9 , fig.width = 12}
mappriorityshelter
```



## 

```{r  echo=FALSE, fig.height = 9, fig.width = 12 }
mapprioritywater
```

This presentation was prepared using
========================================================

 [R statistical platform](http://www.r-project.org/) for the analysis. The script for the analysis is available on the [dtm-analysis repository](https://github.com/unhcr-iraq/dtm-analysis)
 
 Displacement data collected and available for download through the [DTM](http://iomiraq.net/dtm-page)

Please share your comments with UNHCR Iraq Information management Unit @ legoupil.at.unhcr.org